---
title: "introduction"
author: "Chenganji Fan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
```

```{r setup}
library(binomial)
```

## binomial

The package "binomial" is an implementation for for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.
Also there is plot and print implemented so the users can easily visualize the distribution.


## Calculate counts of total possibilities and the probability of binomial

User can always use bin_choose() and bin_probability(). Those two function operates the same as choose() and dbinom(). bin_choose() takees in trials and prob as argument, and bin_probability() has three arguments : success, trials, prob.

```{r}
bin_choose(5,0.5)
bin_probability(1, 5, 0.5)
```

## Calculate distribution and plot it

the package makes it really easy to visualize the distribution by table and plot. User only need to implement trials and prob as argument of functions, and the distribution table will show. By using plot(), user can visualize the distribution even better by generating a barplot.

```{r}
bin <- bin_distribution(5,0.5)
bin
plot(bin)
```

## Calculate the cumulative probability and plot it

in case the user want to see the cumulative probility changes and a plot with single line instead of barplot. the package also provides bin_cumulative() that generates a table with sucess, prob, cumulative. and then user can graph it by calling plot(), which will generate a simple plot that shows the trend of cumulative probability

```{r}
bin1 <- bin_cumulative(5,0.5)
bin1
plot(bin1)
```

##  Set up your own variable

User can create their own variable, and the package will provide description of the variable as well as summary of it.

```{r}
var <- bin_variable(5,0.5)
var
varsum <- summary(var)
varsum
```

## basic function package also provides

the package provides simple function that calculate mean, variance, mode, skewness, kurtosis for binomial. Users can directly use them if wish to.

```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```

